### 2016-01-25 inputs/introduction.tex
Modified introduction

and Random Forest Imputation) with the performance of a method specific 

@@

implemented in the software package Beagle). The relative efficiency of 

@@

accuracy achieved and the computation time required.\\

>>>>

and Random Forest Imputation) with the performance of two methods specific 

@@

implemented in the software package Beagle, %and haplotype reconstruction around the recombination site
and the FILLIN algorithm implemented in the programming suite Tassel). The relative efficiency of 

@@

accuracy achieved and the computation time required. Not only the total imputation accuracy was measured, but also the accuracy of imputing the different genotype classes (major and minor homozygotes, heterozygotes).\\
